Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-04-26 manuscript/supplementaryRW.Rmd
remove in-text citations from FORMIND report supplementary materials

```{=html}
<!--
@article{fischer_lessons_2016,
    title = {Lessons learned from applying a forest gap model to understand ecosystem and carbon dynamics of complex tropical forests},
    volume = {326},
    issn = {03043800},
    url = {https://linkinghub.elsevier.com/retrieve/pii/S0304380015005505},
    doi = {10.1016/j.ecolmodel.2015.11.018},
    language = {en},
    urldate = {2022-09-15},
    journal = {Ecological Modelling},
    author = {Fischer, Rico and Bohn, Friedrich and Dantas de Paula, Mateus and Dislich, Claudia and Groeneveld, J{\"u}rgen and Guti{\'e}rrez, Alvaro G. and Kazmierczak, Martin and Knapp, Nikolai and Lehmann, Sebastian and Paulick, Sebastian and P{\"u}tz, Sandro and R{\"o}dig, Edna and Taubert, Franziska and K{\"o}hler, Peter and Huth, Andreas},
    month = apr,
    year = {2016},
    pages = {124--133},
    file = {Volltext:C\:\\Users\\fischsam\\Zotero\\storage\\EISNTZF6\\Fischer et al. - 2016 - Lessons learned from applying a forest gap model t.pdf:application/pdf},
}
-->
```
A full description of the model can be found in @fischer_lessons_2016.
The basis for the parameterization we applied is described in @bohn2014.

>>>>

A full description of the model can be found in Fischer et al (2016) .
The basis for the parameterization we applied is described in Bohn et al
(2014):

-   Bohn, F. J., Frank, K., & Huth, A. (2014). Of climate and its
    resulting tree growth: Simulating the productivity of temperate
    forests. Ecological Modelling, 278, 9--17.
    <https://doi.org/10.1016/j.ecolmodel.>

-   Fischer, R., Bohn, F., Dantas de Paula, M., Dislich, C., Groeneveld,
    J., Gutiérrez, A. G., Kazmierczak, M., Knapp, N., Lehmann, S.,
    Paulick, S., Pütz, S., Rödig, E., Taubert, F., Köhler, P., &
    Huth, A. (2016).Lessons learned from applying a forest gap model to
    understand ecosystem and carbon dynamics of complex tropical
    forests. Ecological Modelling, 326, 124--133.
    <https://doi.org/10.1016/j.ecolmodel.2015.>
